Verifying Demonstrations

### 2017-08-10 RelatedWork.tex

\mode*
\section{Related work}

@@

>>>>

\mode*
\section{Related work}
\label{RelatedWork}

@@

Another problem for all the above methods is exemplified by the demonstrations 
in Seoul:
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he demonstrators not only gather in open space, but also small 
  alleys and between buildings%
}.
This is difficult to fully capture.
If photo material is taken from angles we will additionally have problems not 
counting people twice.
